---
title: "Interview Attendance Prediction"
output:
  word_document: default
  pdf_document: default
  html_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Include Libraries
```{r}
library(tidyverse)
library(stringr)
library(dplyr)
library(data.table)
library(boot)
require(ISLR)
```
Read File
```{r}
# Read csv
int_csv <- read.csv("c:/Data Science/Final Project/Interview.csv")
int_df <- data.frame(int_csv)
str(int_df)
```
Remove Unwanted columns
```{r}
# Select the columns required for Analysis
int_df <- subset(int_df, select = -c(2,3, 4, 5, 6, 7, 23, 24, 25, 26 ))
names(int_df)
str(int_df)
```
Rename column names to make it easy
```{r}
setnames(int_df, old=c("Candidate.Current.Location","Candidate.Job.Location", "Candidate.Native.location", "Interview.Venue"), new=c("curr_Location", "Job_Location", "Native", "Venue"))
setnames(int_df, old=c("Have.you.obtained.the.necessary.permission.to.start.at.the.required.time"), new=c("Permission"))
setnames(int_df, old=c("Hope.there.will.be.no.unscheduled.meetings", "Can.I.Call.you.three.hours.before.the.interview.and.follow.up.on.your.attendance.for.the.interview", "Can.I.have.an.alternative.number..desk.number..I.assure.you.that.I.will.not.trouble.you.too.much", "Have.you.taken.a.printout.of.your.updated.resume..Have.you.read.the.JD.and.understood.the.same", "Are.you.clear.with.the.venue.details.and.the.landmark.", "Has.the.call.letter.been.shared"), new=c("Unscheduled_Meetings", "Call_before_3hrs", "Alt_no", "Resume_prinout", "Landmark", "Call_letter"))
setnames(int_df, old=c("Expected.Attendance"), new=c("Rec_Expectation"))
names(int_df)
```
Checking each column for unique values

Client Name:
```{r}
unique(int_df$Client.name)
```
Too many names for the same Client - Data Error
Data Correction using "R" string features
Correct "Aon hewitt Gurgaon" to "Hewitt"
```{r}
int_df$Client.name<-str_replace(int_df$Client.name, "Aon hewitt Gurgaon", "Hewitt")
```
correct "Aon Hewitt" to "Hewitt"
```{r}
int_df$Client.name<-str_replace(int_df$Client.name, "Aon Hewitt", "Hewitt")
```
correct "Standard Chartered Bank Chennai" to "Standard Chartered Bank"
```{r}
int_df$Client.name<-str_replace(int_df$Client.name, "Standard Chartered Bank Chennai", "Standard Chartered Bank")
```
Check Current Location column
```{r}
unique(int_df$curr_Location)
# Tidy - trim spaces
int_df$curr_Location <- str_trim(int_df$curr_Location)

#data correct "Gurgaonr" , "Chennai"
int_df$curr_Location <- str_replace(int_df$curr_Location, "Gurgaonr", "Gurgaon")
int_df$curr_Location <- str_replace(int_df$curr_Location, "chennai", "Chennai")
int_df$curr_Location <- str_replace(int_df$curr_Location, "CHENNAI", "Chennai")
unique(int_df$curr_Location)
```
Check Job_Location column
```{r}
unique(int_df$Job_Location)
# Remove Unwanted Spaces - trim padding
int_df$Job_Location <- str_trim(int_df$Job_Location)
```
Check Venue
```{r}
unique(int_df$Venue)
# trim padding
int_df$Venue <- str_trim(int_df$Venue)
```
Check Native
```{r}
unique(int_df$Native)
# Remove spaces - trim padding
int_df$Native <- str_trim(int_df$Native)
unique(int_df$Native)
```
```{r}
attach(int_df)
```
I converted the data as scores, to be used to predict the outcome.

The Data is used to predict if the Candidate will attend the Job Interview or not and to see how many will turn out for the Interview. The columns Current Location(where the Candidate is living), Job Location(where the JOb is located), Venue(where the Interview will be held), Native(Native of the Candidate) were used as indicators. As a general Psychology, many want to stay in their Native. If they are currently working in a different location,they might be interested in a Job Change and would want to attend the interview.

I have created 2 type of Scores - 1 for Logistic Regression Model and another to be be used in Decision Tree Model. Based on the condition, if the likelihood for attending is more, then a '1' or "Yes" is given for score. If the likelihood for attending is less, then a '0' or "No" is given for the score.

Score based on Location:

Loc_score1, Loc_tree1 - Based on the Assumption, When the Current Location is not equal to native, the candidate is likely to go for a job change. 
```{r}
# Loc_score1 - 
for (i in 1:nrow(int_df))
{
  if (Native[i] != curr_Location[i]) 
    int_df$Loc_score1[i] <- 1
  else
    int_df$Loc_score1[i] <- 0
}
table(int_df$Loc_score1)
# Loc_tree1 - Current Location not equal to native
for (i in 1:length(Native))
{
  if (Native[i] != curr_Location[i]) 
    int_df$Loc_tree1[i] <- "Yes"
  else
    int_df$Loc_tree1[i] <- "No"
}
table(int_df$Loc_tree1)
```
Loc_score2, Loc_tree2 - Based on the Assumption, when the Native of the candidate is equal to Job Location, the candidate is likely to go for a Job Change.
```{r}
for (i in 1:length(int_df$Native))
{
  if ((int_df$Native[i] == int_df$Job_Location[i]) )
    int_df$Loc_score2[i] <- 1
  else
    int_df$Loc_score2[i] <- 0
}
table(int_df$Loc_score2)

for (i in 1:length(int_df$Native))
{
  if ((int_df$Native[i] == int_df$Job_Location[i]) )
    int_df$Loc_tree2[i] <- "Yes"
  else
    int_df$Loc_tree2[i] <- "No"
}
table(int_df$Loc_tree2)
```
Loc_score3, Loc_tree3 - Based on the Assumption, when the Native is the same as Venue, the candidate is likely to go for a Job Change.
```{r}
for (i in 1:length(int_df$Native))
{
  if (int_df$Native[i] == int_df$Venue[i])
    int_df$Loc_score3[i] <- 1
  else
    int_df$Loc_score3[i] <- 0
}
table(int_df$Loc_score3)

for (i in 1:length(int_df$Native))
{
  if (int_df$Native[i] == int_df$Venue[i])
    int_df$Loc_tree3[i] <- "Yes"
  else
    int_df$Loc_tree3[i] <- "No"
}
table(int_df$Loc_tree3)
```
The Recruiter checks the Readiness of the Candidate, by asking several questions. These questions were posed to check the Readiness, interest of the Candidate.The more Ready, interested, the more likelihood in attending the interview.

From the question, "Have you obtained the necessary permission to start at the required time", one can understand how much the Candidate is ready for a change.

From my point of view, Yes, NA - shows more interest, may attend interview, Not yet, No, Yet to confirm, nulls - may not attend interview
```{r}
int_df$Permission <- str_trim(int_df$Permission)


int_df <- mutate(int_df, Perm_score =
                   ifelse(grepl("Yes", int_df$Permission), 1,
                          ifelse(grepl("yes", int_df$Permission), 1,
                                 ifelse(grepl("Na", int_df$Permission), 1, 0 
                                 ))))
table(int_df$Perm_score)

# For Decision Tree
int_df <- mutate(int_df, Perm_tree =
                   ifelse(grepl("Yes", int_df$Permission), "Yes",
                          ifelse(grepl("yes", int_df$Permission), "Yes",
                                 ifelse(grepl("Na", int_df$Permission), "Yes", "No" 
                                 ))))
table(int_df$Perm_tree)
```
For the question, "Hope there will be no unscheduled meetings", answers such as "Yes", "Na" are considered as "may attend", "NO", "Not Sure", "Cant say" can be considered as "may not attend"
```{r}
unique(Unscheduled_Meetings)
int_df <- mutate(int_df, Uns_meeting_score =
                   ifelse(grepl("Yes", int_df$Unscheduled_Meetings), 1,
                          ifelse(grepl("No", int_df$Unscheduled_Meetings), 0,
                                 ifelse(grepl("Not Sure", int_df$Unscheduled_Meetings), 0,
                                        ifelse(grepl("Not sure", int_df$Unscheduled_Meetings), 0,
                                               ifelse(grepl("cant Say", int_df$Unscheduled_Meetings), 0,
                                                      ifelse(grepl("yes", int_df$Unscheduled_Meetings), 1,
                                                             ifelse(grepl("Na", int_df$Unscheduled_Meetings), 1, 0
                                                             )
                                                      )))))))
table(int_df$Uns_meeting_score)
```
For Decision Tree
```{r}
int_df <- mutate(int_df, Uns_meet_tree =
                   ifelse(grepl("Yes", int_df$Unscheduled_Meetings), "Yes",
                          ifelse(grepl("No", int_df$Unscheduled_Meetings), "No",
                                 ifelse(grepl("Not Sure", int_df$Unscheduled_Meetings), "Not Sure",
                                        ifelse(grepl("Not sure", int_df$Unscheduled_Meetings), "Not Sure",
                                               ifelse(grepl("cant Say", int_df$Unscheduled_Meetings), "Not Sure",
                                                      ifelse(grepl("yes", int_df$Unscheduled_Meetings), "Yes",
                                                             ifelse(grepl("Na", int_df$Unscheduled_Meetings), "Yes", "No"
                                                             )
                                                      )))))))
table(int_df$Uns_meet_tree)
```
Question: "Can I Call you three hours before the interview and follow up on your attendance for the interview?"
Answers : "Yes", "Na" - considered for "may attend"
        : "No", nulls, "Dont" - considered "may not attend"
```{r}
unique(Call_before_3hrs)
int_df$Call_before_3hrs <- str_trim(int_df$Call_before_3hrs)

int_df <- mutate(int_df, Call_score =
                   ifelse(grepl("Yes", int_df$Call_before_3hrs), 1,
                          ifelse(grepl("No", int_df$Call_before_3hrs), 0,
                                 ifelse(grepl("No", int_df$Call_before_3hrs), 0,
                                        ifelse(grepl("Dont", int_df$Call_before_3hrs), 0,             
                                               ifelse(grepl("yes", int_df$Call_before_3hrs), 1,
                                                      ifelse(grepl("Na", int_df$Call_before_3hrs), 1, 0)))))))
table(int_df$Call_score)

# For Decision Tree

int_df <- mutate(int_df, Call_tree =
                   ifelse(grepl("Yes", int_df$Call_before_3hrs), "Yes",
                          ifelse(grepl("No", int_df$Call_before_3hrs), "No",
                                 ifelse(grepl("No", int_df$Call_before_3hrs), "No",
                                        ifelse(grepl("Dont", int_df$Call_before_3hrs), "No",             
                                               ifelse(grepl("yes", int_df$Call_before_3hrs), "Yes",
                                                      ifelse(grepl("Na", int_df$Call_before_3hrs), "Yes", "No")))))))
table(int_df$Call_tree)
```
Question : Can I have an alternative number/ desk number?     
Answer   : "Yes", "na"
         : "No", nulls

```{r}
unique(Alt_no)
int_df$Alt_no <- str_trim(int_df$Alt_no)
int_df <- mutate(int_df, Alt_score =
                   ifelse(grepl("Yes", int_df$Alt_no), 1,
                          ifelse(grepl("No", int_df$Alt_no), 0,
                                 ifelse(grepl("na", int_df$Alt_no), 1,
                                        ifelse(grepl("yes", int_df$Alt_no), 1,
                                               ifelse(grepl("Na", int_df$Alt_no), 1, 0))))))
table(int_df$Alt_score)

#Alt_tree
int_df <- mutate(int_df, Alt_tree =
                   ifelse(grepl("Yes", int_df$Alt_no), "Yes",
                          ifelse(grepl("No", int_df$Alt_no), "No",
                                 ifelse(grepl("na", int_df$Alt_no), "Yes",
                                        ifelse(grepl("yes", int_df$Alt_no), "Yes",
                                               ifelse(grepl("Na", int_df$Alt_no), "Yes", "No"))))))
table(int_df$Alt_tree)
```
Question : "Have you taken a printout of your updated resume?"
Answer  : "Yes", "Na" - considered "may attend"
        : "No", "Not yet, nulls" - considerd "may not attend"
```{r}
unique(Resume_prinout)
int_df$Resume_prinout <- str_trim(int_df$Resume_prinout)
int_df <- mutate(int_df, Res_score =
                   ifelse(grepl("Yes", int_df$Resume_prinout), 1,
                          ifelse(grepl("No", int_df$Resume_prinout), 0,
                                 ifelse(grepl("Not yet", int_df$Resume_prinout), 0,
                                        ifelse(grepl("Not Yet", int_df$Resume_prinout), 0,
                                               ifelse(grepl("na", int_df$Resume_prinout), 1,
                                                      ifelse(grepl("Na", int_df$Resume_prinout), 1,
                                                             ifelse(grepl("yes", int_df$Resume_prinout), 1, 0))))))))
table(int_df$Res_score)
# Resume_tree
int_df <- mutate(int_df, Res_tree =
                   ifelse(grepl("Yes", int_df$Resume_prinout), "Yes",
                          ifelse(grepl("No", int_df$Resume_prinout), "No",
                                 ifelse(grepl("Not yet", int_df$Resume_prinout), "No",
                                        ifelse(grepl("Not Yet", int_df$Resume_prinout), "No",
                                               ifelse(grepl("na", int_df$Resume_prinout), "Uncertain",
                                                      ifelse(grepl("Na", int_df$Resume_prinout), "Uncertain",
                                                             ifelse(grepl("yes", int_df$Resume_prinout), "Yes", "No"))))))))
table(int_df$Res_tree)
```
Question : Are you clear with the venue details and the landmark?
Ans      : Yes, NA - considered "May Attend"
         : No, nulls - considered "May not Attend"
```{r}
int_df$Landmark <- str_trim(int_df$Landmark)
unique(Landmark)
int_df <- mutate(int_df, Land_score =
                   ifelse(grepl("Yes", int_df$Landmark), 1,
                          ifelse(grepl("No", int_df$Landmark), 0,
                                 ifelse(grepl("na", int_df$Landmark), 1,
                                        ifelse(grepl("Na", int_df$Landmark), 1,
                                               ifelse(grepl("yes", int_df$Landmark), 1, 0))))))

table(int_df$Land_score)

# Land_tree

int_df <- mutate(int_df, Land_tree =
                   ifelse(grepl("Yes", int_df$Landmark), "Yes",
                          ifelse(grepl("No", int_df$Landmark), "No",
                                 ifelse(grepl("na", int_df$Landmark), "Uncertain",
                                        ifelse(grepl("Na", int_df$Landmark), "Uncertain",
                                               ifelse(grepl("yes", int_df$Landmark), "Yes", "No"))))))

table(int_df$Land_tree)
```
Question : Has the call letter been shared?
Answer   : "Yes", "NA" - considered "May Attend"
          : "No", Null, others - considered "may not Attend"
          
```{r}
int_df$Call_letter <- str_trim(int_df$Call_letter)
unique(Call_letter)
int_df <- mutate(int_df, Letter_score =
                   ifelse(grepl("Yes", int_df$Call_letter), 1,
                          ifelse(grepl("na", int_df$Call_letter), 1,
                                 ifelse(grepl("Na", int_df$Call_letter), 1,
                                        ifelse(grepl("yes", int_df$Call_letter), 1, 0)))))

table(int_df$Letter_score)

# Letter_tree
int_df <- mutate(int_df, Letter_tree =
                   ifelse(grepl("Yes", int_df$Call_letter), "Yes",
                          ifelse(grepl("na", int_df$Call_letter), "Uncertain",
                                 ifelse(grepl("Na", int_df$Call_letter), "Uncertain",
                                        ifelse(grepl("yes", int_df$Call_letter), "Yes", "No")))))

table(int_df$Letter_tree)

```
Predictors:
Observed Attendance
```{r}
unique(int_df$Observed.Attendance)
int_df$Observed.Attendance <- str_trim(int_df$Observed.Attendance)

# For Classification Model
int_df <- mutate(int_df, Obs_Att_class =
                   ifelse(grepl("Yes", int_df$Observed.Attendance), 1,
                          ifelse(grepl("yes", int_df$Observed.Attendance), 1,  
                                 ifelse(grepl(" yes", int_df$Observed.Attendance), 1, 0))))
table(int_df$Obs_Att_class)

# For Decision Tree
int_df <- mutate(int_df, Obs_Att_tree =
                   ifelse(grepl("Yes", Observed.Attendance), "Yes",
                          ifelse(grepl("yes", Observed.Attendance), "Yes",  
                                 ifelse(grepl(" yes", Observed.Attendance), "Yes", "No"))))
table(int_df$Obs_Att_tree)

```
Logistic Regression using All variables - Train and Test Dataset, Splitting into 75:25
```{r}
attach(int_df)

set.seed(1)
train = sample(1233, 900)

glm.fit = glm(Obs_Att_class ~ Loc_score1 + Loc_score2 + Loc_score3 +
                Perm_score + Call_score + Uns_meeting_score + Alt_score + 
                Res_score + Land_score + Letter_score + Marital.Status + Gender,
              data=int_df, family = binomial, subset = train)

```

Predict on the train Dataset:
```{r}
glm.probs=predict(glm.fit,type="response")
summary(glm.probs)

glm.pred = rep(0, 900)
glm.pred = ifelse(glm.probs > 0.5,1,0)
str(glm.pred)
str(Obs_Att_class[train])

table(glm.pred, Obs_Att_class[train])

mean(glm.pred == Obs_Att_class[train])


```
Train Error rate: 100 - 71.11 = 29.89%
---------------------------------------
Predict on Test Data set:
```{r}
glm.probs=predict(glm.fit,newdata=int_df[-train,],type="response")
summary(glm.probs)

glm.pred = rep(0, 333)
glm.pred = ifelse(glm.probs > 0.5,1,0)

table(glm.pred, Obs_Att_class[-train])

mean(glm.pred == Obs_Att_class[-train])
```
Test Error Rate: 100 - 66.97 = 33.03%
-------------------------------------
```{r}
summary(glm.fit)
```

Logistic Regression - Fit Smaller model based on significant variables from the regression using all variables. From the summary, we can say Loc_score2, Perm_score, Call_score contribute significantly in the predictions.
```{r}
glm.fit=glm(Obs_Att_class ~ Loc_score2 + Perm_score + Call_score,
            data=int_df, family=binomial, subset=train)

summary(glm.fit)
```
Loc_score2, call score has negative coefficients
```{r}
glm.probs=predict(glm.fit, newdata=int_df[-train,],type="response") 
glm.pred=ifelse(glm.probs >0.5,1,0)
table(glm.pred,Obs_Att_class[-train])
mean(glm.pred==Obs_Att_class[-train])
```
Applying Logistic Regression Model, we would be able to predict 67.26 % correctly about the outcome of the interview.The Questions - "Have you obtained the necessary permission to start at the required time?", "Has the call letter been shared?" attribute mainly to the predictions.



Decision Trees Model was created to check what are the important questions, which could predict the outcome.
```{r}
attach(int_df)
require(tree)

tree.intatt = tree(Obs_Att_class~ Loc_score1 + Loc_score2 + Loc_score3 + 
                     Perm_score + Call_score + Uns_meeting_score + Alt_score +
                     Res_score + Land_score + Letter_score +
                     Marital.Status + Gender, data=int_df, subset = train)
summary(tree.intatt)
```
Regression tree has been created
```{r}
plot(tree.intatt)
text(tree.intatt, pretty=0)
tree.intatt
```
Cross Validation
```{r}
cv.intatt = cv.tree(tree.intatt)
plot(cv.intatt$size ,cv.intatt$dev, type='b')
```
Pruning
```{r}
prune.intatt = prune.tree(tree.intatt, best = 2)
plot(prune.intatt )
text(prune.intatt, pretty= 0)
tree.pred = predict(tree.intatt, newdata=int_df[-train, ])
plot(tree.pred, Obs_Att_class[-train], xlab = "Predicted Attendance", ylab = "Observed Attendance")
abline(0,1)
mean((tree.pred - Obs_Att_class[-train])^2)
```
From applying Decision Trees model, we could say that based on the Question, "Have you obtained the necessary permission to start at the required time", we would be able to predict 73.01% of the actual outcome.